Sa TOB Report

### 2020-05-27 SaPa TOB growth curves clean.Rmd
Added comments from Marvin to figures

#End point bar graph with std error
ggplot() +
  geom_col(data = wilcoxDataGood, aes (x = culture, y = meanLog, fill = antibiotic, group = antibiotic), position = position_dodge( ))+
  geom_linerange(data = wilcoxDataGood, aes(x = culture, ymin = meanLog - seLog, ymax = meanLog + seLog,group = antibiotic),position = position_dodge(width = .9))+
  scale_y_continuous(expand = expand_scale(mult = c(0, 0.05)))+
  labs(title =expression(paste(italic("S. aureus"), " growth at 5 hours")),y = "Log10 CFUs", x = "Culture condition") +
  scale_fill_grey()+
  theme_cowplot()+
  theme_half_open()+
  background_grid()

ggplot() +
  geom_col(data = percentChange %>% filter(sample == "1-25-20"), aes (x = culture, y = MeanLogKill))+
  geom_linerange(data = percentChange, aes(x = culture, ymin = MeanLogKill - SeLogKill/2, ymax = MeanLogKill + SeLogKill/2))+
  scale_y_continuous(expand = expand_scale(mult = c(0, 0.05)))+
  labs(title =expression(paste(italic("S. aureus"), " killing by Tobramycin")),y = "Log10 kill", x = "Culture condition") +
  scale_fill_grey()+
  theme_cowplot()+
  theme_half_open()+
  background_grid()

>>>>

#End point bar graph with std error
tobCFUPlot<-ggplot() +
  geom_col(data = wilcoxDataGood, aes (x = culture, y = meanLog, fill = antibiotic, group = antibiotic), position = position_dodge( ))+
  geom_linerange(data = wilcoxDataGood, aes(x = culture, ymin = meanLog - seLog, ymax = meanLog + seLog,group = antibiotic),position = position_dodge(width = .9))+
  scale_y_continuous(expand = expand_scale(mult = c(0, 0.05)), breaks = c(0,2,4,6,8,10), labels =c(0,2,4,6,8,10))+
  scale_x_discrete(name ="", breaks = c("mono","wt","mut"), labels =c("mono","co w/wild-type",expression("co w/"*Delta*"pqsL")))+
  labs(y = expression(paste(Log[10], " CFU")), x = "", fill = "") +
  scale_fill_grey()+
  theme_cowplot()+
  theme_half_open()+
  background_grid()

tobPercentChangePlot<-ggplot() +
  geom_col(data = percentChange %>% filter(sample == "1-25-20"), aes (x = culture, y = MeanLogKill))+
  geom_linerange(data = percentChange, aes(x = culture, ymin = MeanLogKill - SeLogKill/2, ymax = MeanLogKill + SeLogKill/2))+
  scale_y_continuous(expand = expand_scale(mult = c(0, 0.05)))+
  scale_x_discrete(name ="", breaks = c("mono","wt","mut"), labels =c("mono","co w/wild-type",expression("co w/"*Delta*"pqsL")))+
  labs(y = expression(paste(Log[10], " CFU")), x = "") +
  scale_fill_grey()+
  theme_cowplot()+
  theme_half_open()+
  background_grid()

prow <- plot_grid(tobCFUPlot+theme(legend.position="none"),tobPercentChangePlot+theme(legend.position="none"),align='vh',labels = c("A", "B"),hjust = -1,nrow = 1)
legend <- get_legend(tobCFUPlot + theme(legend.box.margin = margin(0, 0, 0, -6)))
plot_grid(prow,legend,rel_widths = c(3, .4))
```
